Enter our title here

### 2017-08-19 manuscript.tex
Updated bib file with new entries - in future export bib file from mendeley when adding new sources.  Updated tex file with new bibliogrphy style - hopefully this will allow you to compile in RStudio better.
Update manuscript.tex

\documentclass{tise_style}
\usepackage{natbib}

@@

\Abstract{ The text of your abstract.}

\Keywords{one, two, three}

@@

\section{Introduction}
\usepackage{hyperref}

@@

*I'm confused about LearnR and thinks someone else should write about it.*

@@

Check this out, Schubert said this \cite{Schubert13}.

Check this out, Campbell said this \cite{Campbell02} regularly, but cite this in parentheses \citep{Campbell02}.

Check this out, Chi said this \cite{Chi81}.

\bibliographystyle{ECA_jasa}
\bibliography{bibfile}

>>>>

\documentclass{tise_style}
\usepackage{natbib}
%Having trouble getting tise_style to compile correctly in RStudio, will re-run it with this before submission

%-----------------------------------------------------------------------------------------------------
%Substitute this all with tise_style
%\documentclass[12pt]{article}
%\usepackage{natbib}  % used for citations
%\usepackage[parfill]{parskip} %used for formatting style of text
%\usepackage{url}

% Sets margins to 1 in
%\addtolength{\oddsidemargin}{-.5in}%
%\addtolength{\evensidemargin}{-.5in}%
%\addtolength{\textwidth}{1in}%
%\addtolength{\textheight}{1.3in}%
%\addtolength{\topmargin}{-.8in}%
%-----------------------------------------------------------------------------------------------------

@@

@@

\maketitle

\section{Introduction}

@@

*I'm confused about LearnR and think someone else should write about it.*

@@

%Check this out, Schubert said this \cite{Schubert13}.

%Check this out, Campbell said this \cite{Campbell02} regularly, but cite this in parentheses \citep{Campbell02}.

%Check this out, Chi said this \cite{Chi81}.

%Use this for final submission
%\bibliographystyle{ECA_jasa}
\bibliographystyle{Chicago}
\bibliography{library}
